Paper Notes

### 2019-03-24 paper_notes.tex
Normal update

\documentclass{book}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}	% make indent in first paragraph
\usepackage{bm}
\usepackage{geometry}		% to make typesettings like margins
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{hyperref}

\usepackage{natbib}			% to insert citations
\usepackage{xcolor}			% extend the colors can be used
\usepackage{calrsfs}		% caligraphy font family

\usepackage{bibentry}		% package used to insert full citation in body text
\makeatletter 
\renewcommand\BR@b@bibitem[2][]{\BR@bibitem[#1]{#2}\BR@c@bibitem{#2}}
\makeatother
\nobibliography*

@@

\usepackage[english]{babel}
\renewcommand{\baselinestretch}{1.5}

@@

@@

@@

\part{Economics}
\label{part:economics}

\chapter{Econometrics}
\label{cha:econometrics}

@@

@@

@@

@@

@@

\chapter{IO} % (fold)
\label{cha:io}

\section{Data and Techniques} % (fold)
\label{sec:data_and_techniques}

\subsection{Data Source} % (fold)
\label{sub:data_source}

@@

@@

\subsection{Techniques} % (fold)
\label{sub:techniques}

@@

@@

% section data_and_techniques (end)

\section{Rey and Stiglitz, 1995, RAND} % (fold)
\label{sec:rey_and_stiglitz_1995_rand}

>>>>

\documentclass{book}
\usepackage[utf8]{inputenc}

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,pdflscape,subfigure,array,hyperref}

% \usepackage{indentfirst}	% make indent in first paragraph
\setlength\parindent{0pt}
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.5}

\usepackage{bm}
\usepackage{geometry}		% to make typesettings like margins
\usepackage{mathrsfs}
\usepackage{hyperref}

\usepackage{natbib}			% to insert citations
\usepackage[table,xcdraw]{xcolor}			% extend the colors can be used
\usepackage{calrsfs}		% caligraphy font family

\usepackage{bibentry}		% package used to insert full citation in body text

\makeatletter 
\renewcommand\BR@b@bibitem[2][]{\BR@bibitem[#1]{#2}\BR@c@bibitem{#2}}
\makeatother
\nobibliography*

@@

\usepackage[english]{babel}

@@

\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\blue}[1]{{\color{blue} #1}}
\newcommand{\mytitle}[1]{{\large{\textbf{#1}}}}
\newcommand{\mysubtitle}[1]{{\normalsize{\textbf{#1}}}}

@@

% \usepackage{graphicx}
% \usepackage[table,xcdraw]{xcolor}

@@

\part{Econometrics}
\label{part:econometrics}

\chapter{Common Tools} % (fold)
\label{cha:common_tools}

\noindent
\textbf{Seemingly Unrelated Regressions:}
\footnote{see Pinkse notes.}
\begin{itemize}
	\item $y_i=X_i^T\theta_0+u_i$, where $X_i$ is $k$ by 1.
	\item $\hat \theta=(\sum_{i=1}^n{X_i\hat\Psi^{-1} X_i^T})^{-1}
	\sum_{i=1}^n{X_i\hat\Psi^{-1} y_i}$
	\item This estimator is more efficient than OLS. And it only requires the estimation of unconditional variance of error term, while WLS requires the whole distribution of error term conditional on $X_i$. So will also be more efficient than WLS in practice. 
	\item Intuitively, it uses the correlation information of error terms across equations.
	\item Notice, more applicable when $k$ is not very large (relative to $n$). Otherwise the estimation of $\hat \Psi$ will be too demanding.
\end{itemize}

\chapter{Identification} % (fold)
\label{cha:identification}

% chapter identification (end)

\section{Identification in Multi-Equilibria} % (fold)
\label{sec:identification_in_multi_equilibria}

\begin{itemize}
	\item Find some feature that is common to all equilibria. For example, \cite{Berry:1992gl}

	\item Set identification. For example, \cite{Shum:2018hw}
\end{itemize}

% section identification_in_multi_equilibria (end)

@@

\chapter{Moment Inequality} % (fold)
\label{cha:moment_inequality}

\section{PPHI, 15 EMCA} % (fold)
\label{sec:pphi_15_emca}

% section pphi_15_emca (end)

% chapter moment_inequality (end)

@@

\chapter{Others} % (fold)
\label{cha:others}

% chapter others (end)

@@

\section{Gillen-Montero-Moon-Shum, 18 MP} % (fold)
\label{sec:gillen_montero_moon_shum_18mp}

\noindent
\textbf{\bibentry{Gillen:2018bg}}

This paper uses LASSO to pick instruments for BLP style model. They apply it in Mexico voting model.

\vspace{1em}
\noindent
\textbf{Applications:}
\begin{itemize}
	\item Maybe in education choice
\end{itemize}

% section gillen_montero_moon_shum_18mp (end)

@@

\textcolor{red}{Is there any cases where only structural estimation can work, while reduced estimation, no matter how frequently A/B test, can not work?}

Lixiong Li in IO brownbag introduces a way for identification where there is moment restrictions.
The idea is to replace the specific distribution assumptions of the error term by some moment restrictions.
By this, we can not have point identification in many cases, but can get set identification even with very weak conditions.

\textcolor{blue}{I think it a good paper.}

@@

\part{IO} % (fold)
\label{part:io}

\chapter{Data and Techniques} % (fold)
\label{cha:data_and_techniques}

\section{Data Source} % (fold)
\label{sec:data_source}

@@

\noindent
\textbf{Nielson Consumer Panel Dataset}
\begin{itemize}
	\item Penn State has institutional access
\end{itemize}

\noindent
\textbf{ISMS Durable Goods Dataset 1}
\begin{itemize}
	\item \bibentry{Ni:2012in}
\end{itemize}

\noindent
\textbf{Bureau of Transportation Statistics}
\begin{itemize}
	\item \url{https://www.transtats.bts.gov}
\end{itemize}

\noindent
\textbf{Airbnb data}
\begin{itemize}
	\item Penn State Department of Real Estate \textcolor{red}{(?) how to get it}
\end{itemize}

@@

\section{Timber Data by Forest Service} % (fold)
\label{sec:timber_data}

\noindent
\textbf{Timber Industry:}
\begin{itemize}
	\item Dropping off timber, then process timber to log, then process log to lumber by mill
	\begin{itemize}
		\item Loggers do not possess mill machines, so they will sell the dropping timber to mills. At the same time since there are many different kinds of logs (e.g. in diameters), one specific mill may lack the machine for some logs and will resell them in the market. So the resale market after timber auction is frequent. This create a pro-collusion environment.
	\end{itemize}

	\item Timber tracts are very different from one to another. For older timber tracts, the values of bidders are more heterogeneous. For young or second-grow timber tracts, the value is easier to estimate and we can think it more like common value auction.
\end{itemize}

\vspace{1em}
\noindent
\textbf{Databook:}
\begin{itemize}
	\item BDA: number of bidders bid excess reserve price. In sealed auction, must bid larger than reserve price. In ascending auction, must actively bid at least once in auction.

	BDT: number of bidders actually show up in an auction.
	\begin{itemize}
		\item e.g. BDA 0, BDT 1: 1 show up, bid lower than reserve price. Notice that BDA=1 does not mean the auction is not successful.

		\begin{itemize}
			\item See 884F060103002, where BDA=0, BDT=1, the bidding value is the same as advalue, but the status (stt) is 1.
		\end{itemize}
		\item e.g. BDA 3, BDT 6: the price might increase too fast, the remaining 3 don't have a chance to bid.
	\end{itemize}
\end{itemize}

\vspace{1em}
\noindent
\textbf{Research Questions:}
\begin{itemize}
	\item \cite{Athey:2011cs} shows that small bidders (loggers) pay higher in sealed auction. Why they do not move to the ascending auction in this case? Why the arbitrage does not work here?
	\begin{itemize}
		\item Maybe it's easier to collude in ascending auction than in sealed auction. Then independent bidders will prefer to stay at sealed bid auction even the realized price is higher. Because if they move to ascending auction, then they are likely not to win.
	\end{itemize}

	\item What if the reserve price is strategically picked by the auctioneer?

	\item Timber auction is multidimensional. Each tract have different species, and each firm will have different values over this species. Can we use the Nima's optimal multidimensional mechanism design to verify the data?

	\item \textcolor{blue}{Timber firms may have special interest in some species, so they may want to participate in specific auctions. And thus the private value assumption does not hold.}
	\begin{itemize}
		\item Bob: Firms have strong incentive to collude in this case. Firm A prefer species a, firm B prefers species b. Such preference may derive from their specialization in processing, and is commonly known among bidders. Then in an auction where there are 80\% specie a and 20\% specie b, it is very likely that firm A will win and sell species b to firm B after auction.

		\item Then they are very likely to be engaged in an collusion. How can we distinguish it from the pure collusion based rotation mechanism, where firm A will attend in some auctions more frequently while B will attend others?
	\end{itemize}
\end{itemize}

\section{FCC data} % (fold)
\label{sec:fcc_data}

\noindent
\textbf{Related Literature:}
\begin{itemize}
	\item \cite{McMillan:1994bc}

	\item \cite{Cramton2000} clarifies many terms in a narrative way.

	\item \cite{Weber:1997ce} introduces \textit{strategic demand reduction} in simultaneous ascending bidding auctions.
	\begin{itemize}
		\item e.g. Two firms, three objects. Each firm either any one object 100, and any combination 200. Then if one firm take the strategy that keep bidding on two objects until some of which exceeds 100. Then the other firm will find it optimal to bid at the other object. The auction will end at a very low bid for all three objects.
	\end{itemize}

	\item \cite{Krishna:1996fo} discusses payoff complementarity in ascending bidding auction. Their model is based on second price sealed auction.

% subsection fcc_data (end)

% subsection timber_data (end)

\section{Techniques} % (fold)
\label{sub:techniques}

@@

\noindent
\textbf{Google Street View Data:}
\begin{itemize}
	\item \cite{Gebru:2017wk} uses Google Street View data to collect automobile information, and use machine learning to predict socioeconomic conditions of different cities.
\end{itemize}

@@

\chapter{Cartels and Collusion} % (fold)
\label{sec:cartels_and_collusion}

A very good narrative of cartel and bidding rings is from \textit{Economics of Collusion} by Marshall and Marx.
I will briefly summarize.

\begin{itemize}
	\item A cartel in most cases will need explicit agreement instead of just tacit collusion.
	\item They will hire a consulting firm to negotiate the meeting and to keep track of all records.
	\item They will fix a market share instead of just prices, and use `true-up' to redistribute as agreed at the end of the period.
	\item They will also change the incentive of the sales team to avoid over selling.
\end{itemize}

A bidding ring is a group of bidders where they will not compete within the group. 
There are two benefits.
First, competition is directly lowered and price would be lower for bidders.
Second, by reduce bidding within the group they will not leak information to other less informed bidders, and reduce competition indirectly.

\noindent
\textbf{Measure of Concentrations:}
\begin{itemize}
	\item Herfindal Index: 
\end{itemize}

\section{Green and Porter, 84 EMCA} % (fold)
\label{sec:green_and_porter_84_emca}

\textbf{\bibentry{Green_Porter:1984EMCA}}

\cite{Green_Porter:1984EMCA} points out that \textbf{price war can be a part of collusion equilibrium}, challenging the view that price war being a signal of competition.
The key point is that there is \textbf{uncertainty in demand}, which is after the decision of firm's quantity decision.
So firms are unable to distinguish between a low demand shock and someone's possible deviating.

They show that the equilibrium strategy is a \textbf{\textcolor{blue}{trigger strategy with forgiveness}}.
For realized price $p$ higher than some threshold $\bar p$,
firms choose the cooperative quantity;
otherwise they will choose the Cournot quantity for T periods, where the punish time is given (maybe by explicit negotiation process).

The dynamic incentive is very interesting here.
In equilibrium, no firms will have incentive to deviate. 
So the only possibility for a low price is a bad demand shock.
Despite everyone knowing this, they will still choose the Cournot quantity for $T$ periods as a punishment.
This is to give correct dynamic incentive.
Suppose a strategy profile features no punishment even in low price.
Then firms would have incentive to output more since they would not be punished anyway.

\begin{mdframed}[style=comment]
\noindent
\textbf{Learning Process:}

One thing I feel uncomfortable is the information structure of the firm. 
In this paper, firms are assumed to know the realization of price, the distribution of shocks $\theta$, and the function form of price $p()$.

If they do not know the distribution, not do they know the functional form.
Then it would be impossible for them to distinguish the volatility in $\theta$ and in quantity.
Thus it would be impossible to detect probable deviation.
\footnote{In the paper, we can detect deviation at some probability. But even this cannot be satisfied because the distribution is unknown and relative parameters are unidentified.}
\end{mdframed}

\textbf{Identification:} in appendix they show that in principle the collusion behavior can be identified.
But in practice it is generally quite difficult.

% subsection green_and_porter_84_emca (end)

\section{Rotemberg-Saloner, 86 AER} % (fold)
\label{sec:rotemberg_saloner_86_aer}

\textbf{\bibentry{RotembergSaloner:86aer}}
\vspace{1em}

\cite{RotembergSaloner:86aer} also tries to explain price war, but they show that \textbf{price wars are more likely to happen during the demand boom instead of doom.}
In their model, firms make decisions \textit{after} realization of shocks.
So firms can distinguish between the price drop by deviation and price drop by low demand.
Then their result is quite intuitive.
It is more profitable to deviate when demand is high.
So the collusive price at high demand should be lower, the lower is collusive price, the less attractive to deviate.

\vspace{1em}
\noindent
\textit{Comments:}
\begin{itemize}
	\item With more specific assumption on knowledge of firm, they can say more about the competition structure.
	In \cite{Green_Porter:1984EMCA}, the only reasonable competition mode is Cournot.
	But both Bertrand and Cournot are appropriate in this paper.
	\item The establishment of price competition equilibrium is skillful.
	They first assume a exogenous punishment to generate optimal decision, then use such decision to generate an actual punishment.
	This constitutes a fixed point argument.
	\footnote{Same trick as in \cite{Peters_Siow:2002dx} small market case.}

	\item This model is `\textit{really about countercyclical pricing---firms have perfect information and adjust prices smoothly in response to demand conditions.}'(by \cite{Ellison:94RAND} p.38).
	There is no \textit{regime shift} like in \cite{Green_Porter:1984EMCA} since the past has no uncertainty.
	\begin{itemize}
		\item It is not important whether the future has uncertainty. Say, the demand is seasonal and is certain. It won't change the result, the pricing will still be countercyclical. Intuitively, what the firms compare is the current deviation profit and expected future gain, thus future uncertainty is not important (as long as firms are risk neutral).
	\end{itemize}
\end{itemize}

\section{Porter, 83 Bell} % (fold)
\label{sec:porter_83_bell}

\textbf{\bibentry{Porter:83bell}}

\cite{Porter:83bell} is specifically to test \cite{Green_Porter:1984EMCA} using JEC data.
\footnote{Joint Executive Committee, which is widely used since it records the cartel in 1880-1886 for the train industry in US.}

\vspace{2mm}
\noindent
\textbf{Estimation Strategy:}
\vspace{-0.5em}
\begin{itemize}
	\item \textbf{Goal} is to test whether regime switch happens in supply side, and to identify when such switches happen.
	This paper does not test whether firms actually play the equilibrium as described by \cite{Green_Porter:1984EMCA}, but only describes the reversion pattern.
	\item \textbf{Data} is aggregate time series price and quantity.
	\begin{itemize}
		\item KZ: notice there is some internal inconsistency in this setting. Porter assumes 1) no secret deviation, without giving justification; 2) homogeneous good, which is largely due to data limitation; and 3) firms do price competition. But then we should see prices near marginal cost, which should not fluctuate a lot.
	\end{itemize}

	\item \textbf{Firm Strategy:} The firms in JEC actually use price instead of quantity as strategic variable, and they use differentiated products (through different service). This is different from \cite{Green_Porter:1984EMCA} model.
	\begin{itemize}
		\item But in econometrics model part, this paper seems to still assume the quantity competition. This may due to the data limitation --- they only have aggregated price and quantity.
		\item Firm's decision problem is summarized by 
		\[p_t(1+\theta_{it}/\alpha_t)=MC_i(q_{it})\]
		Porter notes that this form can encompass Bertrand competition, Cournot competition and perfect collusion, with $\theta_{it}$ being 0, $(0,1)$, 1 respectively.
		\textcolor{red}{This seems reasonable, what I don't understand is how it can be compatible with Green-Porter's model? In their model it is obvious that Cournot is the only possible way of competition.}

		\begin{mdframed}[style=comment]
			This form can be derived from firm profit maximization. Suppose \[\pi_i(q_i,q_{-i}) =p(q_1,\dots,q_n)q_i-C(q_i) \]
			by taking derivative w.r.t. $q_i$ we will get:
			\[p(1+\frac{1}{\varepsilon_{q_i,p}})=MC(q_i)\]
			Also notice that this can actually encompass both Cournot and Bertrand. In Cournot, we have $p(q_1,\dots,q_n)=p(\sum_{i=1}^nq_i)$; and in Bertrand we have $p(q_1,\dots,q_n) = p(\sum q'|q' \in \max\{q_1,\dots,q_n\},0=q_i\notin q')$

		\end{mdframed}
		\item In firm optimization problem, there is no uncertainty. But in turning it to reduced form, the paper has to add error term $U_{2t}$ to match the data. In adding this term, we implicitly assume 1) firms do not know this shock when making decision; 2) this shock is aggregate for all firms (?).
	\end{itemize}
	\item \textbf{Estimation:}
	\begin{itemize}
		\item Demand Curve:
		\item Supply Curve:
		\item Simultaneous Equation System:
		\item Conditional pdf:
		\item Unconditional pdf:
		\item Convergence algorithm:
	\end{itemize}
\end{itemize}

% subsection porter_83_bell (end)

% subsection rotemberg_saloner_86_aer (end)

\section{Genesove-Mullin, 01 AER} % (fold)
\label{sec:genesove_mullin_01_aer}

\textbf{\bibentry{Genesove:2001jz}}

\cite{Genesove:2001jz} narratively describes how the sugar cartel in 1930-1936 actually works.
They find cartel's action deviates from what collusion theory predicted.
The main idea they try to convey is: \textbf{collusion is more a contraction problem than a market structure problem}.

Questions they want to answer:
\begin{itemize}
	\item How firms coordinate their pricing?
	\begin{itemize}
		\item Mainly through rules, and by ordinary meetings to adjust to rules. Such meetings are necessary due to the uncertain nature of competition environment.
	\end{itemize}
	\item How prevalent is cheating? What's the punishment?
	\begin{itemize}
		\item Cheating is not discussed in neither \cite{Green_Porter:1984EMCA} nor \cite{RotembergSaloner:86aer}. There the price war is just an equilibrium result, and no one has incentive to `secretly cheat'.
		\item But in reality cheat actually happens. Because contract is always incomplete and firms have many tricks to escape. But retaliation does not always happen. They will first make some effort to partially identify a cheat and a bad draw, e.g. by asking the suspect to show some hard evidence. When the cartel is convinced that someone has cheated, they are mostly likely to take tit-for-tat strategy instead of trigger.
	\end{itemize}
\end{itemize}

Below are notes taken during the reading.

\begin{itemize}
	\item Cartel mainly collude through rules.
	\begin{itemize}
		\item Open prices and publicly announced items
		\item Prior notification
		\begin{itemize}
			\item Complementary to open announcement. Ensure that firms can potentially retaliate before consumers react.
		\end{itemize}
		\item Restrictions on contractual practices between the refiners and downstream firms
		\begin{itemize}
			\item Mainly to eliminate discriminatory pricing
			\item Very detailed and standardized. Because `every contractual term can mask a price cut'. The standardized model is implicitly assumed in Green-Porter, though homogeneous good and the extremely simplified contract and strategy form.
			\item Such rigidity is also costly to cartel
		\end{itemize}
		\item Alternative explanation for such limitation on contracts:
		\begin{itemize}
			\item Limiting non-price competition
			\item Authors did not agree. They argue that the \textit{contractual harmonization} conveys more than non-price competition limitation.
		\end{itemize}
	\end{itemize}
	\item Collusion contract is always incomplete
	\begin{itemize}
		\item The regular and frequent meetings are to fix the holes
	\end{itemize}

	\item Why firms do not directly retaliate when they find cheating?
	\begin{itemize}
		\item Different from \cite{Green_Porter:1984EMCA}, firms in Sugar Cartel can argue within the institute meeting. Such meeting gives them a chance to figure out whether it is a shock or a intentional cheat. In other words, firms do have a choice to reduce the confounding uncertainty, which reduces their incentive to retaliate.
	\end{itemize}
	\item Firms do not retaliate to every cheating. They do not use massive retaliation unless the cheating is very high. The retaliation they take generally is `matching', kind of tit-for-tat.
	\begin{itemize}
		\item One reason to desist from full-scale retaliation (as in \cite{Green_Porter:1984EMCA}) is the vertical contractual arrangement in the industry. Firms sell sugar through brokers. Brokers will have much higher incentive to deviate since their number is much larger than that of firms. Such structure made deviation more prevalent. It is also more costly, since one more layer of brokers make it more difficult for firms to switch between two pricing regimes.
	\end{itemize}
	\item Firms rarely react to market share.
	\begin{itemize}
		\item Market share is too noisy a signal.
	\end{itemize}
	\item Firms choose to meet frequently to adapt quickly to external change, and to fix any holes in rule as soon as possible. They seem not care much about the \textit{renegotiation problem}.
\end{itemize}

% subsection genesove_mullin_01_aer (end)

\section{Graham-Marshall, 87 JPE} % (fold)
\label{sec:graham_marshall_87_jpe}

\textbf{\bibentry{Graham_Marshall:87jpe}}

This paper models the collusion within bidders in Second Price Sealed auction and English auction in IPV framework.
They find collusion strategy equilibrium can be stable in such settings.
Coalition of any size is stable, and the expected payoff to each member increases with the coalition size.

\begin{itemize}
	\item In second price auction. The optimal reserve price is a increasing function of coalition size.
	\item In English auction. The optimal reserve price is identical to that of second price auction, and independent of observed highest bid. This result is striking since it seems at first that auctioneer at English auction can do better with this additional information.
\end{itemize}

Some stylized facts are not incorporated in this model:
\begin{itemize}
	\item Fact: brokers will not be invited to the coalition. If a broker has a customer, his willingness to pay is much stronger than any dealer. Thus he does not want to join the ring since other ring members will push price high in the knock-out round. If a broker does not have a customer, the he is not really coming to bid but to share the `ring hat'. The ring does not want him in this case.

	$\rightarrow$ This fact cannot be encompassed in this model. Because the model assumes IPV, while brokers represent a very special distribution (0 or very high) of value, against the assumption.
\end{itemize}

\section{MMRS, 94 GEB} % (fold)
\label{sec:marshall_meurer_richard_stromquist_94_geb}

\textbf{\bibentry{Marshall:1994bc}}

This paper raises a algorithm to numerically solve equilibrium in heterogeneous auctions.
And they use this algorithm to investigate simulate some facts for auction coalition in first price auction.

\vspace{1em}
\noindent
\textbf{Facts from Simulation:}
\begin{itemize}
	\item Revenue equivalence of first price auction (or Dutch) and second price auction (or English) does not hold in existence of collusion. The expected revenue is higher in first price auction.

	\item In second price auction, the individual has no incentive to deviate from the coalition even when coalition size is very large. Actually the surplus of coalition gain to individual gain increases with coalition size $k_1$.

	\item In first price auction, the individual has no incentive to deviate when coalition size is small, but does have incentive to deviate when coalition size is large. The relative advantage of individual bidder increases with coalition size $k_1$.

	\item In ascending auction, for any given value, the weaker bidder will be more aggressively than stronger bidder. 
	\begin{itemize}
		\item This induces inefficiency. Stronger bidder with higher value may lose the auction.
		{\color{blue}
		\item Payoff equivalence not holding in this environment?
		\begin{itemize}
			\item maybe sealed auction and ascending auction does not reduce to the same direct mechanism in this environment
		\end{itemize}
		}
	\end{itemize}

	\item The same features are also found in \cite*{Athey:2011cs}. Although in Athey el al., the heterogeneity is not from collusion but from different cost distribution between large (mill) and small (logger) bidders. But the mathematical representation is the same, larger bidders value distribution FOSD that of the small bidders.
	\begin{itemize}
		\item They find the timber auction has following stylized facts: sealed first price auction attract more small bidders, shit the allocation toward these bidders, and can generate higher revenue to auctioneer.
	\end{itemize}
\end{itemize}

% subsection marshall_meurer_richard_stromquist_94_geb (end)

% subsection graham_marshall_87_jpe (end)

% section cartels_and_collusion (end)

\chapter{Price Dispersion} % (fold)
\label{cha:price_dispersion}

\section{Butters, 77 RES} % (fold)
\label{sec:butters_77_res}

\textbf{\bibentry{butters:77res}}

This paper tries to generate price dispersion in a homogeneous environment. Homogeneity is in the sense that commodity characteristics, consumer preference, seller cost are all the same. The only heterogeneity comes from seller's strategy on pricing and advertisement.

Unlike previous literature only focusing on consumer side, Butters models both consumer search behavior and the firm strategy. In other words, previous models are `partial-partial equilibrium', while this paper is `partial equilibrium'.

\vspace{1em}
\noindent
\textbf{No Consumer Search:}
\begin{itemize}
	\item Seller: decide the amount of ads, for each ad can post a different price. Each ads costs $b$.
	\item Buyer: the only way to purchase is through ads, and pick the lowest price (unless all prices higher than reserved price $m$). Each ads reach each consumer with equal probability, that's to say, the probability distribution of number of ads of any given consumer is Poison distribution. Most importantly, the probability that a consumer receives no price quotes lower than $p$, given the ads distribution $A(p)$, is $exp(-A(p))$.
	\item The model is solved purely at market level. Denote $A(p)$ to be the number of ads with prices equal or lower than $p$ divided by consumer number $M$. $S(p)$ to be the sales actually happen with price lower than $p$ divided by consumer number $M$. $\pi(p)$ be the probability of selling a good by pricing at $p$.
	\begin{itemize}
		\item We thus have $s(p)=a(p)\pi(p)$, where $s(p),a(p)$ are derivatives of $S,A$ respectively.
		\item The profit function is:
		\[\text{profit}=\int{[(p-p_0)\pi(p)-b]a(p)}dp\]
	\end{itemize}
	\item By no deviation condition, the marginal profit at any equilibrium price level should be zero. Thus, $(p-p_0)\pi(p)=b$, and $\pi(p)=b/(p-p_0)$
	\item By similar arguments as in allpay auction, the equilibrium price can only be a range $[p_0+b,m]$
	\item IMPORTANT: $\pi(p)=exp(-A(p))$
	\begin{itemize}
		\item $\pi(p)$ is the probability that an ad with price $p$ being accepted. This is the probability that this ad goes to a consumer with ZERO price quotes lower than $p$. By our previous analysis, $A(p)$ is the number of ads per consumer, i.e. the single time probability that a consumer receives an ad with price lower than $p$. Then by the results of Poison distribution, the probability that a consumer receiving no price quotes lower than $p$ is $exp(-A(p))$.
		\item This is important since it connects the individual behavior and market index. Firms only cares about $\pi$ when making ads decision; while $A(p)$ can induce $\pi(p)$. These two have to be consistent in equilibrium.
	\end{itemize}
	\item The equilibrium is easy to solve with above characterization.
\end{itemize}

\vspace{1em}
\noindent
\textbf{With Consumer Search:}
\begin{itemize}
	\item The setting is quite tricky. The equilibrium is greatly simplified due to the following two assumptions of \textit{word-of-mouth search}:
	\begin{itemize}
		\item ASSP-1: The probability that a search yield an offer from any particular seller is proportional to his share in total shares;
		\item ASSP-2: The probability that this offer is at a price within a particular interval $(p_1,p_2)$ is proportional to the seller's sale at this particular interval.
	\end{itemize}
	Above two assumptions makes the profit from searching consumers exactly proportional to that of non-searching consumers. So we only need to maximize the profit from non-searching consumers, which has the same structure as no-search case.
	\begin{itemize}
		\item KZ: I find these two assumptions uncomfortable. This is not about the search behavior, but all about the optimal advertisement.
	\end{itemize}

	\item Claim: consumers will search iff they receive no ads, and in this case they will accept the first price they find.
	\begin{itemize}
		\item The second half is direct implication of the assumptions, especially assumption 2.
		\item For first half, denote the highest posted price $p_{max}$, and the threshold price of searching $p_c$. Obviously $p_{max}\leq p_c$. Further we claim that $p_{max}=p_c$, otherwise the firm can increasing highest posted price by $\varepsilon$ while keep advertisement same as in $p_{max}$.
	\end{itemize}

	\item The equilibrium is very similar to no-search case. The only difference is $\pi(p_{min})=1/\phi>1$. At lowest posted price, one ad will induce more than one purchase.
	\begin{itemize}
		\item This is because now we have $1-\phi$ portion of people receive no ads, at any price interval. Thus conditional on the consumer receiving at least one ad, $p_{min}$ will for sure lead them to buy. But such ads will induce even more purchase because those receiving no ad will also buy from this seller at this price $p_{min}$ proportionally.
		\item This makes sense because since consumer can search, firms can transfer the load of advertisement partly to the consumer side.
	\end{itemize}

	\item The portion $\phi$ can be pinned down in equilibrium by the fact that eventually every consumer will buy.
\end{itemize}

\section{Sorensen, 00 JPE} % (fold)
\label{sec:sorensen_00_jpe}

\textbf{\bibentry{Sorensen:00jpe}}

\vspace{1em}
\noindent
\textbf{Facts and Identification Strategy:}
\begin{itemize}
	\item This paper is a reduced form paper testing price distribution in drugs.

	\item The identification strategy is to \textbf{use \textit{frequency} as the key explanation variable}. 
	\begin{itemize}
		\item This is the \textit{comparative static} approach. Because by \cite{butters:77res} the price dispersion will shrink if the cost of search is lower. Here the searching frequency is a proxy as search cost.
	\end{itemize}

	\item Measure of price dispersion is \textbf{price range}. This is an absolute measure, because search cost generally do not vary with price scale. There are other measures possible, for example standard deviation, or relative range.

	\item The environment is carefully picked for clean identification:
	\begin{itemize}
		\item The market is some small isolated markets, with sufficiently many pharmacies within each market.
		\item The frequency of purchase is determined by instruction of doctor, which is uncontrollable by drug consumers.
		\item The drug price is posted, thus is in principal public so that econometricians can collect them. But consumers have to pay the search cost to gain such information.
		\item All pharmacies face similar cost.
	\end{itemize}

	\item They also exclude the possibility of heterogeneous pharmacy service.
	\begin{itemize}
		\item First, they show that pharmacies have very different rankings for different drug price. This fact is inconsistent with the explanation of pharmacy level heterogeneity.
		\item Second, they run a residual regression to show that pharmacy heterogeneity at most account for 30\% of price dispersion.
	\end{itemize}
\end{itemize}

\vspace{1em}
\noindent
\textbf{What Cannot be Answered:}
\begin{itemize}
	\item The data generating process. How exactly search cost affects the price dispersion.
	\item Quantifying search cost.
	\item This has to be done with a structural model like \cite{Hortacsu:2004bg}.
\end{itemize}

% subsection sorensen_00_jpe (end)

\section{Hortacsu-Syverson, 04 QJE} % (fold)
\label{sec:hortacsu_syverson_04_qje}

\textbf{\bibentry{Hortacsu:2004bg}}

\vspace{1em}
\noindent
\textbf{Facts and Explanations:}
\begin{itemize}
	\item Mutual fund prices are hugely dispersed, despite their financial homogeneity. The 75th to 25th price ratio of Index Funds is 3.1;
	\item Nonportaforlio Differentiation. Funds attributes like manager tenure, the age of the fund, rate of taxable distributions will not directly affect return, but do affect investors' choice.
	\begin{itemize}
		\item Only focus on vertical differentiation and assume homogeneous preference over these attributes. Because horizontal differentiation is unidentifiable from search cost differences.
	\end{itemize}
	\item Search Cost.
	\item Switch Cost. If switch cost is important, then we should observe in data that inflow/outflow of S\&P Fund in a non-load funds family should be less volatile than those in a load funds family. Because when index fund performs poor, those in a load fund family will switch to another fund in the same fund family, inducing larger imbalance within the fund family. This is not significant in data.
\end{itemize}

\vspace{1em}
\noindent
\textbf{Model:}
\begin{itemize}
	\item Funds are different in both prices and other vertical attributes. But investors have homogeneous utility form. 
	\footnote{We cannot identify taste heterogeneity using BLP. The taste differentiation is unidentifiable with search cost differentiation.}
	We assume a specific utility form, where price enters linearly:
	\[u_j=W_j \beta-p_j+\varepsilon_j\]
	\item Investors have cost $c_i$ for each search, which is distributed in population as $G(c)$. An investor searches sequentially until the expected utility gain is smaller than search cost:
	\[c_i \leq \int_{u^*}^{\bar u} (u-u^*)dH(u)\]
	where $H(u)$ is investors' belief about the distribution about funds' indirect utility, which is unknown to econometricians and have to be assumed. We assume that funds provide $N$ levels of utility, $u_1 < ... <u_N$. If we further assume equal sampling probabilities, we have:
	\[H(u)=\frac{1}{N}\sum_{j=1}^N I[u_j \leq u]\]
	Investors are assumed to know the value of each $u_j$, they are only uncertain about which fund provides which utility level.
	\begin{itemize}
		\item KZ: this assumption very strong, which greatly reduces the dimension of information investors need to learn about.
	\end{itemize}
	\item The optimal search rule yields critical points in search cost:
	\[c_j=\sum_{k=j}^N{\rho_k (u_k-u_j)}\]
	where $\rho_k$ is the probability that fund $k$ is sampled on each search, which is known to all investors. The RHS is the expected payoff of another search conditional on already found $j$. Thus $c_j$ is the highest possible search cost that could allow such search.
	\begin{itemize}
		\item KZ: $\rho_k$ is just the density of $H(u)$. If equal sampling, then $\rho_k=1/N$ for all $k$. If not equal sampling, it should be conditional on how much time an investor has already searched, unless we assume the funds pool is infinite. 
	\end{itemize}
\end{itemize}

\vspace{1em}
\noindent
\textbf{Identification:}
\begin{itemize}
	\item \textbf{Goal:} identify the search cost and coefficients of other attributes with only price and market share data.
	\item Funds market share can be written in cost thresholds. Thinking of $u_1$ with lowest indirect utility. Only those with really high search cost will end up buying fund-1, and they have to be unlucky to draw this fund at the first time.
	\[q_1=\rho_1(1-G(c_1))=\rho_1\Big[1-G\Big(\sum_{k=1}^N{\rho_k(u_k-u_1)}\Big)\Big]\]
	For fund-2, there are two sources. One investor may have cost higher than $c_1$ and draw fund-2 in the first time; or he has cost $c_2<c<c_1$ and draw fund-2 first time or directly after fund-1.
	\footnote{$Pr=\rho_2+\rho_1\rho_2+\rho_1\rho_1\rho_2+...=\rho_2/(1-\rho_1)$}
	\[q_2 = \rho_2(1-G(c_2))+\frac{\rho_2}{1-\rho_1}(G(c_2)-G(c_1)) \tag{7}\]
	Similarly, we can write $N$ equations for all funds market share. 
	\begin{itemize}
		\item Thus we can back out $G(c_j)$ with known $\rho_j$ and $q_j$ for all $j$.
		Moreover, we can normalize $G(c_N)=0$ because we have $c_N=0$ by threshold equation, and search cost have to be nonnegative.
		\item We can take derivative with $p_j$, because $c_j$ is influenced by $u_j$ which contains $p_j$. Thus we can write $N-1$ derivatives:
		\[\frac{\partial q_j}{\partial p_j}
		=f(\rho_1,...,\rho_N,g(c_1),...,g(c_j)) \tag{10}\]
		where $g(c_j)$ is the p.d.f. of cost distribution at $c_j$.
	\end{itemize}
